Suplementary Material 2: Drawing Publication Plots

### 2023-03-31 S1_replicate_stats_and_plots.Rmd
visual adjustments to plots

### Fig 1A: Estonian vs TwinR Full Data

@@

```{r, fig.height=11.7/2, fig.width=8.3}
infoTxt <- "model prediction with 95% CI and data mean SE"
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE[dmm_EE$births_total <17, ],
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=1,
                 position = position_nudge(x = -0.1),
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_EE_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data,
             aes(y = estimate,  x=births_total, color="9 W-European"),  size = 1) +
    stat_summary(data=dmm_orig[dmm_orig$births_total <19, ],
                 aes(x=births_total, y=prob_twin,
                     color="9 W-European", fill="9 W-European"),
                 alpha=1,
                 shape = 1,
                 position = position_nudge(x = 0.1),
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_orig_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="9 W-European"),
                alpha = 0.1) +
    ggplot2::scale_x_continuous(breaks = 1:18) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian() +
    labs(subtitle = paste0("(A) All births, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

### Fig 1B: Estonian vs Others No Last Birth

@@

```{r, fig.height=11.7/2, fig.width=8.3}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE_nl_plot,
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=1,
                 fun.data=mean_se,
                 position = position_nudge(x = -0.1)) +
    geom_ribbon(data=fig2_EE_plot_data_nl,
                aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data_nl,
             aes(y = estimate,  x=births_total, color="9 W-European"),  size = 1) +
    stat_summary(data=dmm_orig_nl_plot,
                 aes(x=births_total, y=prob_twin,
                     color="9 W-European", fill="9 W-European"),
                 alpha=1,
                 shape = 1,
                 fun.data=mean_se,
                 position = position_nudge(x = 0.1)) +
    geom_ribbon(data=fig2_orig_plot_data_nl,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="9 W-European"),
                alpha = 0.1) +
    ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian(ylim=c(0,0.03)) +
    labs(subtitle = paste0("(B) Without last birth, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

fig2a <- draw_fig_4C(fig4C_orig_plot_data) + 
  labs(subtitle = "(A) 9 W-European pop., all births")

fig2b <- draw_fig_4C(fig4C_EE_plot_data) + 
  labs(subtitle = "(B) Estonia, all births")

fig2c <- draw_fig_4C(fig4C_orig_nl_plot_data, y_lims = c(0.01, 0.035)) + 
  labs(subtitle = "(C) 9 W-European pop., without last birth")

fig2d <- draw_fig_4C(fig4C_EE_nl_plot_data,y_lims = c(0.01, 0.035)) + 
  labs(subtitle = "(D) Estonia, without last birth")

>>>>

### Fig 1a: Estonian vs TwinR Full Data

@@

```{r, fig.height=11.7/2, fig.width=8.3}
infoTxt <- "model prediction with 95% CI and data mean SE"
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE[dmm_EE$births_total <17, ],
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=1,
                 position = position_nudge(x = -0.1),
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_EE_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data,
             aes(y = estimate,  x=births_total, color="9 W-European"),  size = 1) +
    stat_summary(data=dmm_orig[dmm_orig$births_total <19, ],
                 aes(x=births_total, y=prob_twin,
                     color="9 W-European", fill="9 W-European"),
                 alpha=1,
                 shape = 1,
                 position = position_nudge(x = 0.1),
                 fun.data=mean_se) +
    geom_ribbon(data=fig2_orig_plot_data,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="9 W-European"),
                alpha = 0.1) +
    ggplot2::scale_x_continuous(breaks = 1:18) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian() +
    labs(subtitle = paste0("(a) All births, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

### Fig 1b: Estonian vs Others No Last Birth

@@

```{r, fig.height=11.7/2, fig.width=8.3}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
              aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
    stat_summary(data=dmm_EE_nl_plot,
                 aes(x=births_total, y=prob_twin, color="Estonia", fill = "Estonia"),
                 alpha=1,
                 fun.data=mean_se,
                 position = position_nudge(x = -0.1)) +
    geom_ribbon(data=fig2_EE_plot_data_nl,
                aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                    color="Estonia", fill = "Estonia"),
                alpha = 0.3) + 
    geom_line(data=fig2_orig_plot_data_nl,
             aes(y = estimate,  x=births_total, color="9 W-European"),  size = 1) +
    stat_summary(data=dmm_orig_nl_plot,
                 aes(x=births_total, y=prob_twin,
                     color="9 W-European", fill="9 W-European"),
                 alpha=1,
                 shape = 1,
                 fun.data=mean_se,
                 position = position_nudge(x = 0.1)) +
    geom_ribbon(data=fig2_orig_plot_data_nl,
                aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                    fill="9 W-European"),
                alpha = 0.1) +
    ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
    ggplot2::scale_y_continuous(breaks = seq(0,0.03, by=0.005)) +
    ggplot2::coord_cartesian(ylim=c(0,0.03)) +
    labs(subtitle = paste0("(b) Without last birth, ", infoTxt),
         y="Per-birth twin. prob.",
         x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=8) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "population")

@@

fig2b <- draw_fig_4C(fig4C_orig_plot_data) + 
  labs(subtitle = "(b) 9 W-European, all births")

fig2a <- draw_fig_4C(fig4C_EE_plot_data) + 
  labs(subtitle = "(a) Estonia, all births")

fig2d <- draw_fig_4C(fig4C_orig_nl_plot_data, y_lims = c(0.01, 0.035)) + 
  labs(subtitle = "(d) 9 W-European, without last b.")

fig2c <- draw_fig_4C(fig4C_EE_nl_plot_data,y_lims = c(0.01, 0.035)) + 
  labs(subtitle = "(c) Estonia, without last birth")

### 2023-03-31 S2_draw_publication_plots.Rmd
visual adjustments to plots

fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
            aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
  geom_ribbon(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  color="Estonia", fill = "Estonia"),
              alpha = 0.3) + 
  geom_line(data=fig2_orig_plot_data,
            aes(y = estimate,  x=births_total, color="9 W-European populations"),  size = 1) +
  geom_ribbon(data=fig2_orig_plot_data,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  fill="9 W-European populations"),
              alpha = 0.3) +
  ggplot2::scale_x_continuous(breaks = 1:18) + 
  ggplot2::scale_y_continuous(trans = "logit",
                              breaks = seq(0.005, 0.025, by = 0.001)) +
  ggplot2::coord_cartesian() +
  labs(subtitle = "(A) Complete datasets",
       y="Per-birth twinning probability",
       x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=5, legend_pos = c(0.5,0.9)) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")

@@

```{r}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
            aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
  geom_ribbon(data=fig2_EE_plot_data_nl,
              aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                  color="Estonia", fill = "Estonia"),
              alpha = 0.3) + 
  geom_line(data=fig2_orig_plot_data_nl,
            aes(y = estimate,  x=births_total, color="9 W-European populations"),  size = 1) +
  geom_ribbon(data=fig2_orig_plot_data_nl,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  fill="9 W-European populations"),
              alpha = 0.3) +
  ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
  ggplot2::scale_y_continuous(trans = "logit",
                              breaks = seq(0.005, 0.025, by = 0.001)) +
  labs(subtitle = "(B) Without last births",
       y="Per-birth twinning probability",
       x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=5, legend_pos = "none") + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")

>>>>

fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data,
            aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
  geom_ribbon(data=fig2_EE_plot_data,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  color="Estonia", fill = "Estonia"),
              alpha = 0.3) + 
  geom_line(data=fig2_orig_plot_data,
            aes(y = estimate,  x=births_total, color="9 W-European populations"),  size = 1) +
  geom_ribbon(data=fig2_orig_plot_data,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  fill="9 W-European populations"),
              alpha = 0.3) +
  ggplot2::scale_x_continuous(breaks = 1:18) + 
  ggplot2::scale_y_continuous(trans = "logit",
                              breaks = seq(0.005, 0.025, by = 0.001)) +
  ggplot2::coord_cartesian() +
  labs(subtitle = "(a) Complete datasets",
       y="Per-birth twinning probability",
       x="Maternal total births")
p2 <- fig2_ext_orig + base_theme(larger=5, legend_pos = c(0.5,0.9)) + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")

@@

```{r}
fig2_ext_orig <- ggplot() +  
  geom_line(data=fig2_EE_plot_data_nl,
            aes(y = estimate,  x=births_total, color="Estonia"),  size = 1) +
  geom_ribbon(data=fig2_EE_plot_data_nl,
              aes(y = estimate, x=births_total, ymin = lwr, ymax = upr,
                  color="Estonia", fill = "Estonia"),
              alpha = 0.3) + 
  geom_line(data=fig2_orig_plot_data_nl,
            aes(y = estimate,  x=births_total, color="9 W-European populations"),  size = 1) +
  geom_ribbon(data=fig2_orig_plot_data_nl,
              aes(y = estimate,  x=births_total, ymin = lwr, ymax = upr,
                  fill="9 W-European populations"),
              alpha = 0.3) +
  ggplot2::scale_x_continuous(breaks = 1:18, limits = c(1,NA)) + 
  ggplot2::scale_y_continuous(trans = "logit",
                              breaks = seq(0.005, 0.025, by = 0.001)) +
  labs(subtitle = "(b) Without last births",
       y="Per-birth twinning probability",
       x="Maternal total births")
p3 <- fig2_ext_orig + base_theme(larger=5, legend_pos = "none") + scale_color_manual(values=bc) + 
  scale_fill_manual(values=bc) + guides(color="none") + labs(fill = "")
